Optimization of the Walking Compass Gait Robot With the Use of Control Co-Design

### 2024-05-15 R0_journal/main.tex
bib

\title{Research project title}
\author{Max Howell}
\institute{University Of Tennessee Knoxville$^*$ ($^*$corresponding author),
          \email{mhowel30@vols.utk.edu} \\
        \\
          \at MABE, University of Tennessee, Knoxville,
          \at Nathan W. Dougherty Engineering Building, 1512 Middle Dr, Knoxville, TN 37916\\
}

@@

\begin{document}
\bibliographystyle{plain}
\bibliography{references}

@@

\section{Introduction}
% introduce control-codesign
Control Co-Design (CCD) is a design method used to optimally design a system's parameters and control the system at the same time. Traditionally in engineering,
when a system is designed an iterative process is used to determine the best parameters for the system; however, this can be time consuming and inefficient. 
It has been shown in \cite{} that the cost of control can be decreased by atleast xx\% in systems such as a cartpole pendulum and a quadrotor by using CCD. CCD applications range
from design optimizatoin of (examples of CCD being used with citations)

@@

\begin{figure}[!h]
\centering
\includegraphics[width=10cm]{./figures/compassgaitmodel.png}
\caption{Schematic of the compass gait model. Angles $\theta_{sw}$ and $\theta_{st}$ are shown as the swing leg angle and stance leg angle, respectively.}
\label{fig:compassgaitmodel}
\end{figure}

@@

The dynamic equations of the swing stage of the compass gait, from \cite{french confrence}, can be written in standard planar manupular dynamics form. 
This is shown in \ref{eq:swingeqn}, where $\mb{M}$, $\mb{N}$, and $\mb{G}$ are matrices shown in the appendix, and $\mb{U}$
 is the vector used to apply the torque to each leg, shown in
\ref{eq:U}.

@@

In order to acheive co-design with a simple passive compass gait system, an optimization problem was proposed.
This optimization problem, outlined in Figure \ref{fig:optsetup}, involved maximizing the point mass at the hip ($m_H$) in order to simulate the
compass gait robot "carrying" a heavy object. In order to acheive this goal, the lengths below and above the leg point mass, a and b, were optimized.
The leg point mass ($m$) also changed based on the total length of the legs based on the given density of the legs.

\begin{figure}[!h]
\centering
\includegraphics[width=6cm]{./figures/opt1prob.png}
\caption{Outline of the simple passive optimization problem. The goal is to incrase the range of stable initial conditions while maximizing the applied hip mass.}
\label{fig:optsetup}
\end{figure}

@@

\begin{table}[h]
\centering
\caption{Initial Conditions and System Parameters of the Non-Optimized Compass Gait Shown in \ref{fig:nonoptlimcycle}}
\begin{tabular}{lr}
\toprule
Parameter & Value \\
\midrule
$m (kg)$ & 8.96 \\
$m_H (kg)$ & 80 \\
$a (m)$ & 0.83 \\
$b (m)$ & 0.957 \\
\bottomrule
\end{tabular}
\label{tab:optparam}
\end{table}

@@

Since the hip mass was no longer part of the cost function, it was chosen to also 
be a design variable of the system. The constraints of the system remained the same, outlined in Figure \ref{fig:OLprob}.

\begin{figure}[h]
\centering
\includegraphics[width=7cm]{./figures/openloopcontrol.png}
\caption{The torque and total time to complete a cycle were minimized in the active open loop CCD problem.}
\label{fig:OLprob}
\end{figure}

@@

\begin{table}[h]
\centering
\caption{Average Time per Cycle and Total Time for 10 Cycles of Each Simulation (seconds)}
\begin{tabular}{ccc}
\toprule
Simulation & Average Time/Cycle & Total Time \\
\midrule
Passive System & 0.680 & 6.8 \\
Active System Without Co-Design & 0.594 & 5.94 \\
System with CCD & 0.531 & 5.31\\
\end{tabular}
\label{tab:time}
\end{table}

@@

\begin{table}[h]
\centering
\caption{Summation of $\tau^2$ for the CCD and Open Loop Control System}
\begin{tabular}{lr}
\toprule
System & $\sum \tau^2$ \\
\midrule
Active System Without Co-Design & 133.46\\
System with CCD & 29.17\\
\end{tabular}
\label{tab:tautot}
\end{table}

@@

Shown in this appendix is a more complete version of the dynamics equations of the compass gait. The swing stage dynamics can be written in standard planar manipulator 
dynamics form, shown in \ref{eq:swingeq}. The $\mb{M}$, $\mb{N}$, $\mb{G}$, and $\mb{U}$ matrices are also shown in \ref{eq:M}, \ref{eq:N}, \ref{eq:G}, and \ref{eq:U} respectively.

@@

\begin{equation}
\mb{U} = 
\label{eq:U}
\begin{bmatrix}
\\1\\
\\-1\\
\\0\\
\\0\\
\end{bmatrix}
\end{equation}

@@

>>>>

\title{Optimization of the Walking Compass Gait Robot With the Use of Control Co-Design}
\author{Max Howell}
\institute{University Of Tennessee Knoxville$^*$ ($^*$corresponding author),
          \email{mhowel30@vols.utk.edu} \\
        \\
          \at MABE, University of Tennessee, Knoxville,
          \at Nathan W. Dougherty Engineering Building, 1512 Middle Dr, Knoxville, TN 37916\\
}

@@

\begin{document}

@@

\section{Introduction}
% introduce control-codesign
Control Co-Design (CCD) is a design method used to optimally design a system's parameters and control the system at the same time. Traditionally in engineering,
when a system is designed an iterative process is used to determine the best parameters for the system; however, this can be time consuming and inefficient. 
It has been shown in \cite{wu2022control} that CCD can be used to improve the weight reduction of a high-acceleration precision motion system by 42$\%$, and 
the bandwith of the system by 28$\%$. It has also been shown in \cite{Mandali2023} that CCD can be used to control other non-mechancial such as thermal 
management systems.

@@

\begin{figure}[!h]
\centering
\includegraphics[width=8cm]{./figures/compassgaitmodel.png}
\caption{Schematic of the compass gait model. Angles $\theta_{sw}$ and $\theta_{st}$ are shown as the swing leg angle and stance leg angle, respectively.}
\label{fig:compassgaitmodel}
\end{figure}

@@

The dynamic equations of the swing stage of the compass gait, from \cite{goswami:inria-00073701}, can be written in standard planar manupular dynamics form. 
This is shown in \ref{eq:swingeqn}, where $\mb{M}$, $\mb{N}$, and $\mb{G}$ are matrices shown in the appendix, and $\mb{U}$
 is the vector used to apply the torque to each leg, shown in
\ref{eq:U}.

@@

In order to acheive co-design with a simple passive compass gait system, an optimization problem was proposed.
This optimization problem, outlined in  \ref{eq:optprobsetup}, involved maximizing the point mass at the hip ($m_H$) in order to simulate the
compass gait robot "carrying" a heavy object. In order to acheive this goal, the lengths below and above the leg point mass, a and b, were optimized.
The leg point mass ($m$) also changed based on the total length of the legs based on the given density of the legs.

\begin{equation}
\begin{aligned}
\text{Objective: Maximize $m_H$}\\
\text{Subject to:}\\
\text{Dynamic Constraints of System}\\
\text{Design Variables: 0.1$<$a$<$1, 0.1$<$b$<$1, (m)}\\
\text{Hip Mass: 5$<$$m_H$$<$80, (kg)}\\
\text{Leg Mass: } m = 5(a+b), \text{(kg)}\\
\text{End States $x_1$ and $x_2$ are Constrained Based on Trajectory Generation}
\end{aligned}
\label{eq:optprobsetup}
\end{equation}

@@

\begin{table}[h]
\centering
\caption{Optimized System Parameters of the compass gait.}
\begin{tabular}{lr}
\toprule
Parameter & Value \\
\midrule
$m (kg)$ & 8.96 \\
$m_H (kg)$ & 80 \\
$a (m)$ & 0.83 \\
$b (m)$ & 0.957 \\
\bottomrule
\end{tabular}
\label{tab:optparam}
\end{table}

@@

Since the hip mass was no longer part of the cost function, it was chosen to also 
be a design variable of the system. The constraints of the system remained the same, outlined in \ref{eq:OLprob}.

\begin{equation}
\begin{aligned}
\text{Minimize: } J = \int_{0}^{t} (\tau / \tau_r)^2 + (t/t_r) \,dt \\
\text{Subject to:}\\
\text{Dynamic Constraints of System}\\
\text{Design Variables: } 0.1<a<1 (m), 0.1<b<1 (m), 0<m_H<100 \text{kg}\\
\text{Leg Mass: } m = 5(a+b)\\
\text{End States of $x_1$ and $x_2$ Constrained by Trajectory Generation}
\end{aligned}
\label{eq:OLprob}
\end{equation}

@@

\begin{table}[h]
\centering
\caption{Average Time per Cycle and Total Time for 10 Cycles of Each Simulation (seconds)}
\begin{tabular}{cccc}
\toprule
Simulation & Average Time/Cycle & Total Time & Percent Improvement\\
\midrule
Passive System & 0.680 & 6.8 & N/A\\
Active System Without Co-Design & 0.594 & 5.94 & 12.66$\%$ \\
System with CCD & 0.531 & 5.31 & 21.91$\%$\\
\end{tabular}
\label{tab:time}
\end{table}

@@

\begin{table}[h]
\centering
\caption{Summation of $\tau^2$ for the CCD and Open Loop Control System}
\begin{tabular}{ccc}
\toprule
System & $\sum \tau^2$ & Percent Improvement \\
\midrule
Active System Without Co-Design & 133.46 & N/A\\
System with CCD & 29.17 & 78.1$\%$\\
\end{tabular}
\label{tab:tautot}
\end{table}

@@

Shown in this appendix is a more complete version of the dynamics equations of the compass gait. The swing stage dynamics can be written in standard planar manipulator 
dynamics form, shown in \ref{eq:swingeq}. The $\mb{M}$, $\mb{N}$, $\mb{G}$, and $\mb{U2}$ matrices are also shown in \ref{eq:M}, \ref{eq:N}, \ref{eq:G}, and \ref{eq:U} respectively.

@@

\begin{equation}
\mb{U} = 
\label{eq:U2}
\begin{bmatrix}
\\1\\
\\-1\\
\\0\\
\\0\\
\end{bmatrix}
\end{equation}

@@

\bibliography{bib/references}
\bibliographystyle{plain}
